**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-05-09 Manuscripts/Manuscript v5/Manuscript_AM_v5.Rmd
working on Posthocs
Time as factor does follow the trend?

#linear model
lm1<-lm(StO2_sim ~ Day + Group + Day * Group, data = dat_sim)

@@

summary(glht(lm1, linfct=mcp(Group="Tukey", interaction_average=TRUE)))

@@

>>>>

#linear model
lm1<-lm(StO2_sim ~ factor(Day) + Group + factor(Day) * Group, data = dat_sim)

@@

summary(glht(lm1, linfct = mcp(Group = 'Tukey')))
summary(glht(lm1, linfct=mcp(Group="Tukey", interaction_average=TRUE)))

@@

What does this mean?
https://stats.stackexchange.com/questions/377609/rm-anova-time-as-continuous-or-categorical

If you treat time as a factor then you do get the changes over time!
